\documentclass[12pt,a4paper,sans,italian]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvtheme[blue]{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
%\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                     % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75,a4paper]{geometry}
\usepackage[italian]{babel}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Enrico}
\familyname{Berni}
\title{Curriculum Vitae}                               % optional, remove/comment the line if not wanted
%\address{Via Ippolito Rosellini, 15}{Pisa}{}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty
%\mobile{+39 340 8421977}                          % optional, remove/comment the line if not wanted
%\phone{}                           % optional, remove/comment the line if not wanted
%\fax{}                             % optional, remove/comment the line if not wanted
\email{enricoberni1999@gmail.com}                               % optional, remove/comment the line if not wanted
\homepage{enricoberni.github.io}                         % optional, remove/comment the line if not wanted
%\extrainfo{}                 % optional, remove/comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{some quote}                                 % optional, remove/comment the line if not wanted
%
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Educazione}
\cventry{2013 - 2018}{Maturità Scientifica}{Liceo Scientifico "G.Marconi"}{Grosseto}{100/100 con Lode}{}  % arguments 3 to 6 can be left empty
\cventry{2018 - 2022}{Laurea Triennale in Matematica}{Università di Pisa}{Pisa}{106/110}{}
\cventry{2022 - }{Laurea Magistrale in Matematica}{Università di Pisa}{Pisa}{}{}
%\cventry{2025 - 2030}{PhD in Mathematics}{Temple University}{Philadelphia, PA}{}{}
\section{Tesi triennale}
\cvitem{Titolo}{An Introduction to the Theory of Stable Cohomology Operations}
\cvitem{Relatore}{Prof. Filippo Gianluca Callegaro}
\section{Tesi magistrale}
\cvitem{Titolo}{Bounded Cohomology of Pinched Negatively Curved 3-Manifolds with Positive Cheeger Constant}
\cvitem{Relatore}{Prof. Roberto Frigerio}
%\cvitem{description}{Short thesis abstract}
\section{Altre attività}
%\subsection{Vocational}
\cventry{Feb. 2025 - Giu. 2025}{Docente, Informatica}{ITCS "Filippo Pacini"}{Pistoia}{}{Vincitore di bando di interpello.}
\cventry{Aprile 2025}{Manifolds and Groups in Bologna III}{}{Bologna}{}{Conferenza di geometria in bassa dimensione e teoria geometrica dei gruppi organizzata dal Dipartimento di Matematica dell'Università di Bologna.}
\cventry{Set. 2024 - Nov. 2024}{Docente, Matematica e Fisica}{Liceo Scientifico "Amedeo di Savoia, Duca di Aosta"}{Pistoia}{}{Vincitore di bando di interpello.}
\cventry{Settembre 2024}{LiT II: Lost in Topology}{}{Pisa}{}{Conferenza internazionale di geometria e topologia organizzata dal Centro di Ricerca Matematica "Ennio De Giorgi", Scuola Normale Superiore.}
\cventry{2023 - 2024, 2024 - 2025}{Tutor del corso "Algebra Lineare A"}{}{}{}{Vincitore del bando di concorso bandito dal Dipartimento di Fisica dell'Università di Pisa. Vinto di nuovo per l'anno accademico 2024-2025.}
\cventry{Gennaio 2024}{RGAS School on Singularities}{}{Siviglia, Spagna}{}{Scuola di geometria algebrica organizzata dal Dipartimento di Matematica "Antonio De Castro Brzezicki", Università di Siviglia.}
\cventry{2022 - 2024}{Ciclo di seminari di geometria "Seminari dei baby-geometri"}{}{Pisa}{}{Partecipante}
\cventry{2020 - 2022}{Rappresentante degli studenti}{Dipartimento di Matematica, UniPi}{}{}{Consiglio di Dipartimento, Consiglio di Corso di Studi, Giunta di Dipartimento}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}
%\section{Lingue}
%\cvitemwithcomment{Inglese}{C1}{Conseguita certificazione C1 nel 2016, coltivato nel tempo.}
%\cvitemwithcomment{Language 2}{Skill level}{Comment}
%\cvitemwithcomment{Language 3}{Skill level}{Comment}
\section{Lingue e linguaggi di programmazione}
\cventry{Italiano}{Madrelingua}{}{}{}{}  % arguments 3 to 6 can be left empty
\cventry{Inglese}{Livello avanzato, IELTS 8.0/9}{}{}{}{}
\cventry{Spagnolo}{Livello intermedio}{}{}{}{}
\cventry{\LaTeX}{Livello avanzato}{}{}{}{}
\cventry{C}{Livello intermedio}{}{}{}{}
\cventry{C++}{Livello intermedio}{}{}{}{}
\cventry{HTML}{Livello intermedio}{}{}{}{}
\end{document}
