\documentclass[12pt,a4paper,sans,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvtheme[blue]{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
%\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75,a4paper]{geometry}
\usepackage{babel}
\usepackage{amsfonts}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{\textcolor{black}{Enrico}}
\familyname{\textcolor{black}{Berni}}
\title{Curriculum Vitae}                               % optional, remove/comment the line if not wanted
%\address{Via Vangile, 101}{Massa e Cozzile (PT)}{}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty
%\mobile{+39 340 8421977}                          % optional, remove/comment the line if not wanted
%\phone{}                           % optional, remove/comment the line if not wanted
%\fax{}                             % optional, remove/comment the line if not wanted   % optional, remove/comment the line if not wanted
\email{enrico.berni@temple.edu}   % optional, remove/comment the line if not wanted
\homepage{enricoberni.github.io}    % optional, remove/comment the line if not wanted
%\extrainfo{}                 % optional, remove/comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{some quote}                                 % optional, remove/comment the line if not wanted
%
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Education}
\cventry{From 2025}{PhD Student in Mathematics}{Temple University}{Philadelphia, PA}{}{}
\cventry{2022 - 2025}{Master's Degree in Mathematics}{University of Pisa}{Pisa, Italy}{110/110 cum Laude}{}  % arguments 3 to 6 can be left empty
\cventry{2018 - 2022}{Bachelor's Degree in Mathematics}{University of Pisa}{Pisa, Italy}{106/110}{}
\cventry{2013 - 2018}{High School Diploma}{Liceo Scientifico "G.Marconi"}{Grosseto, Italy}{100/100 cum Laude}{}
\section{Master's Thesis}
\cvitem{Title}{Bounded Cohomology of Pinched Negatively Curved 3-Manifolds with Positive Cheeger Constant}
\cvitem{Advisor}{Prof. Roberto Frigerio}
\cvitem{Abstract}{Building on some works of Bonahon, Canary, Kim-Kim, and Soma, this thesis connects three invariants of infinite-volume, pinched negatively curved 3-manifolds: the bounded fundamental class, the Cheeger constant, and the geometry type of the ends.}
\section{Bachelor's Thesis}
\cvitem{Title}{An Introduction to the Theory of Stable Cohomology Operations}
\cvitem{Advisor}{Prof. Filippo Gianluca Callegaro}

\section{Workshops and Conferences}
\cventry{September 2025}{Hyperbolic Manifolds in Dimensions 4 and More}{}{Montréal, QC, Canada}{}{Workshop on hyperbolic geometry, organized by the Centre de Recherches Mathématiques in Montréal.}
\cventry{April 2025}{Manifolds and Groups in Bologna III}{}{Bologna, Italy}{}{Workshop on low-dimensional geometry and geometric group theory, organized by the Department of Mathematics of the University of Bologna.}
\cventry{September 2024}{LiT II: Lost in Topology}{}{Pisa, Italy}{}{Workshop in geometry and topology, organized by the "Ennio De Giorgi" research centre of the Scuola Normale Superiore.}
\cventry{January 2024}{RGAS School on Singularities}{}{Sevilla, Spain}{}{Winter school in Algebraic Geometry, organized by the Mathematics Institute of the University of Sevilla.}

\section{Talks}
\cventry{Spring 2026}{Geography of Simplicial Volumes of Closed Hyperbolic 3-Manifolds}{Temple University}{Philadelphia, PA, USA}{Junior Geometry Seminar}{}
\cventry{Spring 2026}{A Classification for Group Actions on the Circle}{Temple University}{Philadelphia, PA, USA}{Junior Geometry Seminar}{}
\cventry{Spring 2026}{A Crash Course on Amenable Groups}{Temple University}{Philadelphia, PA, USA}{Graduate Seminar}{}
\cventry{Fall 2025}{Classification of Compact Surfaces through Bilinear Forms over $\mathbb{F}_2$}{Temple University}{Philadelphia, PA, USA}{Graduate Seminar}{}
\cventry{Fall 2025}{Bounded Cohomology, Cheeger Constants and End Geometry}{Temple University}{Philadelphia, PA, USA}{Junior Geometry Seminar}{}
\cventry{Fall 2025}{Mostow Rigidity through Simplicial Volume}{Temple University}{Philadelphia, PA, USA}{Junior Geometry Seminar}{}

\section{Teaching}
\cventry{Spring 2026}{Teacher, Lab for Precalculus}{Temple University}{Philadelphia, PA, USA}{}{Twice-weekly recitations for Precalculus}
\cventry{Fall 2025}{Grader, Intermediate Algebra}{Temple University}{Philadelphia, PA, USA}{}{}
\cventry{Feb. 2025 - Jun. 2025}{Teacher, Computer Science}{ITCS "Filippo Pacini"}{Pistoia, Italy}{}{Winner of CV-based public call}
\cventry{Sep. 2024 - Dec. 2024}{Teacher, Mathematics and Physics}{Liceo Scientifico "Amedeo di Savoia, Duca di Aosta"}{Pistoia, Italy}{}{Winner of CV-based public call}
\cventry{2023 - 2024, 2024 - 2025}{Teaching Assistant for the course "Algebra Lineare A"}{}{}{}{Winner of a merit-based call for recitations and exam grading, paid by the Department of Physics of the University of Pisa. Won again for the 2024-2025 academic year.}
\section{Other experiences}
\cventry{2020 - 2022}{Student Representative}{Department of Mathematics, UniPi}{}{}{Department Council, Faculty Board, Department Junta}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}

\section{Languages spoken}
\cventry{Italian}{Native speaker}{}{}{}{}  % arguments 3 to 6 can be left empty
\cventry{English}{Proficient, IELTS 8.0/9}{}{}{}{}
\end{document}
